Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-06-02 _tex/paper2.tex
Built site for gh-pages

Beyond these potential benefits, the approach offers two additional
advantages. First, it clarifies the roles and interactions of all actors
and processes involved in CJ experiments. Second, it shifts the analytic
paradigm from passively accepting the assumptions of the BTL model to
actively testing their fit with observed data. Together, these
advantages establish a principled framework for evaluating best
practices in CJ experimental designs, one that better aligns with the
demands of contemporary CJ assessment contexts \citep{Kelly_et_al_2022},
offering new insights into existing research and opening promising
avenues for future inquiry. Five current and new research avenues
deserve particular attention due to their direct impact on the
reliability and validity of trait estimates and the accuracy of
statistical inferences. The following sections outline these avenues and
explain how our model provides a rigorous research framework to
investigate them.

\subsection{The impact of sampling and comparison mechanisms on CJ
outcomes and inference robustness}\label{sec-discussion_RA1}

@@

\subsection{The effects of judges' bias on the reliability of
traits}\label{sec-discussion_RA2}

@@

\subsection{The identification of `misfitting' judges and
stimuli}\label{sec-discussion_RA3}

@@

\subsection{The effects of hierarchies on experimental design and
inference}\label{sec-discussion_RA4}

@@

\subsection{The effects of non-dichotomous outcomes and multidimensional
traits on CJ experiments}\label{sec-discussion_RA5}

>>>>

Beyond these potential benefits, the approach offers two additional
advantages. First, it clarifies the roles and interactions of all actors
and processes involved in CJ experiments. Second, it shifts the analytic
paradigm from passively accepting the assumptions of the BTL model to
actively testing their fit with observed data. Together, these
advantages establish a principled framework for evaluating best
practices in CJ experimental designs, one that better aligns with the
demands of contemporary CJ assessment contexts \citep{Kelly_et_al_2022},
offering new insights into existing research and opening promising
avenues for future inquiry.

\subsection{Future research}\label{sec-discussion_RA}

Five current and new research avenues deserve particular attention due
to their direct impact on the reliability and validity of trait
estimates and the accuracy of statistical inferences. The following
sections outline these avenues and explain how our model provides a
rigorous research framework to investigate them.

\subsubsection{The impact of sampling and comparison
mechanisms}\label{sec-discussion_RA1}

@@

\subsubsection{The effects of judges' bias on the reliability of
traits}\label{sec-discussion_RA2}

@@

\subsubsection{The identification of `misfitting' judges and
stimuli}\label{sec-discussion_RA3}

@@

\subsubsection{The effects of hierarchies on experimental design and
inference}\label{sec-discussion_RA4}

@@

\subsubsection{The effects of non-dichotomous outcomes and
multidimensional traits on CJ experiments}\label{sec-discussion_RA5}
